The 2014 SMT Competition

### 2015-08-07 2014/report/SMTCOMP.tex
Layout tweaks to avoid overfull LaTeX boxes.

\begin{table}
\begin{tabular}{|l|lll|}
\hline
Logic & Unique contribution & & \\
\hline
ALIA & 0.4253 [Z3] & 0.4080 CVC4 & 0.1667 veriT \\
AUFLIA & 0.3889 CVC4 & 0.2778 [Z3] & 0.2222 CVC3 \\
AUFLIRA & 0.2615 [Z3] & 0.2521 CVC4 & 0.2503 CVC3 \\
AUFNIRA & 0.2509 [Z3] & 0.2506 CVC4 & 0.2497 CVC3 \\
LIA & 0.3949 [Z3] & 0.3514 CVC4 & 0.2319 CVC3 \\
LRA & 0.3070 CVC4 & 0.3070 [Z3] & 0.2895 CVC3 \\
NIA & 0.8333 [Z3] & 0.1667 CVC4 & 0.0000 Yices2 \\
NRA & 0.5071 [Z3] & 0.4929 CVC4 & 0.0000 Yices2 \\
QF\_ABV & 0.1147 Yices2 & 0.1146 Boolector-just... & 0.1144 Boolector-dual... \\
QF\_ALIA & 0.2235 Yices2 & 0.2235 SMTInterpol & 0.2235 [Z3] \\
QF\_AUFBV & 0.2635 [MathSAT] & 0.2635 CVC4 & 0.2500 Yices2 \\
QF\_AUFLIA & 0.1996 Yices2 & 0.1996 [MathSAT] & 0.1996 CVC4 \\
QF\_AX & 0.2000 Yices2 & 0.2000 [MathSAT] & 0.2000 CVC4 \\
QF\_BV & 0.1051 Boolector & 0.0976 STP-Crypto... & 0.0934 abziz\_min\_features \\
QF\_IDL & 0.2893 [Z3] & 0.2731 Yices2 & 0.2395 CVC4 \\
QF\_LIA & 0.1620 [CVC4-with-bugfix] & 0.1610 [Z3] & 0.1610 SMTInterpol \\
QF\_LRA & 0.1772 CVC4 & 0.1689 Yices2 & 0.1678 SMTInterpol \\
QF\_NIA & 0.4990 [Z3] & 0.4912 AProVE & 0.0084 CVC3 \\
QF\_NRA & 0.7714 [Z3] & 0.1347 CVC3 & 0.0898 CVC4 \\
QF\_RDL & 0.2734 Yices2 & 0.2431 veriT & 0.2431 [Z3] \\
QF\_UF & 0.1451 Yices2 & 0.1449 veriT & 0.1446 CVC4 \\
QF\_UFBV & 0.4140 Yices2 & 0.3172 [Z3] & 0.1720 [MathSAT] \\
QF\_UFIDL & 0.2708 Yices2 & 0.2708 [Z3] & 0.2309 CVC4 \\
QF\_UFLIA & 0.1698 Yices2 & 0.1698 [MathSAT] & 0.1698 CVC4 \\
QF\_UFLRA & 0.1715 [Z3] & 0.1681 Yices2 & 0.1681 [MathSAT] \\
QF\_UFNIA & 0.5000 CVC4 & 0.5000 [Z3] & 0.0000 Yices2 \\
QF\_UFNRA & 0.5802 [Z3] & 0.2099 CVC4 & 0.2099 CVC3 \\
UF & 0.4921 CVC4 & 0.1988 [Z3] & 0.1759 CVC3 \\
UFIDL & 0.5204 [Z3] & 0.4796 CVC4 & 0.0000 Yices2 \\
UFLIA & 0.4069 CVC4 & 0.3502 [Z3] & 0.2425 veriT \\
UFLRA & 0.2857 [Z3] & 0.2381 CVC4 & 0.2381 veriT \\
UFNIA & 0.4156 [Z3] & 0.3860 CVC4 & 0.1984 CVC3 \\
\hline
\end{tabular}
\caption{Contribution from each solver (top 3)}
\label{tab:cont}
\end{table}

>>>>

\begin{table}
\centering\begin{tabular}{|l|lll|}
\hline
Logic & Unique contribution & & \\
\hline
ALIA & 0.4253 [Z3] & 0.4080 CVC4 & 0.1667 veriT \\
AUFLIA & 0.3889 CVC4 & 0.2778 [Z3] & 0.2222 CVC3 \\
AUFLIRA & 0.2615 [Z3] & 0.2521 CVC4 & 0.2503 CVC3 \\
AUFNIRA & 0.2509 [Z3] & 0.2506 CVC4 & 0.2497 CVC3 \\
LIA & 0.3949 [Z3] & 0.3514 CVC4 & 0.2319 CVC3 \\
LRA & 0.3070 CVC4 & 0.3070 [Z3] & 0.2895 CVC3 \\
NIA & 0.8333 [Z3] & 0.1667 CVC4 & 0.0000 Yices2 \\
NRA & 0.5071 [Z3] & 0.4929 CVC4 & 0.0000 Yices2 \\
QF\_ABV & 0.1147 Yices2 & 0.1146 Boolector-just... & 0.1144 Boolector-dual... \\
QF\_ALIA & 0.2235 Yices2 & 0.2235 SMTInterpol & 0.2235 [Z3] \\
QF\_AUFBV & 0.2635 [MathSAT] & 0.2635 CVC4 & 0.2500 Yices2 \\
QF\_AUFLIA & 0.1996 Yices2 & 0.1996 [MathSAT] & 0.1996 CVC4 \\
QF\_AX & 0.2000 Yices2 & 0.2000 [MathSAT] & 0.2000 CVC4 \\
QF\_BV & 0.1051 Boolector & 0.0976 STP-Crypto... & 0.0934 abziz\_min\_f... \\
QF\_IDL & 0.2893 [Z3] & 0.2731 Yices2 & 0.2395 CVC4 \\
QF\_LIA & 0.1620 [CVC4-...fix] & 0.1610 [Z3] & 0.1610 SMTInterpol \\
QF\_LRA & 0.1772 CVC4 & 0.1689 Yices2 & 0.1678 SMTInterpol \\
QF\_NIA & 0.4990 [Z3] & 0.4912 AProVE & 0.0084 CVC3 \\
QF\_NRA & 0.7714 [Z3] & 0.1347 CVC3 & 0.0898 CVC4 \\
QF\_RDL & 0.2734 Yices2 & 0.2431 veriT & 0.2431 [Z3] \\
QF\_UF & 0.1451 Yices2 & 0.1449 veriT & 0.1446 CVC4 \\
QF\_UFBV & 0.4140 Yices2 & 0.3172 [Z3] & 0.1720 [MathSAT] \\
QF\_UFIDL & 0.2708 Yices2 & 0.2708 [Z3] & 0.2309 CVC4 \\
QF\_UFLIA & 0.1698 Yices2 & 0.1698 [MathSAT] & 0.1698 CVC4 \\
QF\_UFLRA & 0.1715 [Z3] & 0.1681 Yices2 & 0.1681 [MathSAT] \\
QF\_UFNIA & 0.5000 CVC4 & 0.5000 [Z3] & 0.0000 Yices2 \\
QF\_UFNRA & 0.5802 [Z3] & 0.2099 CVC4 & 0.2099 CVC3 \\
UF & 0.4921 CVC4 & 0.1988 [Z3] & 0.1759 CVC3 \\
UFIDL & 0.5204 [Z3] & 0.4796 CVC4 & 0.0000 Yices2 \\
UFLIA & 0.4069 CVC4 & 0.3502 [Z3] & 0.2425 veriT \\
UFLRA & 0.2857 [Z3] & 0.2381 CVC4 & 0.2381 veriT \\
UFNIA & 0.4156 [Z3] & 0.3860 CVC4 & 0.1984 CVC3 \\
\hline
\end{tabular}
\caption{Contribution from each solver (top 3)}
\label{tab:cont}
\end{table}
